\documentclass[notitlepage,12pt]{../../cpsc250l}

\title{CPSC 250L Lab 1\\[0.5em] File/Directory Structure and Git Intro\\[0.5em]Name: $\rule{7cm}{0.15mm}$  Section:$\rule{2cm}{0.15mm}$}

\begin{document}

\maketitle

\section{Introduction}

The focus of this lab is to solidify your understanding of file/directory structure, and
introduce you to navigating via the command line interface (CLI).

In lab we will be using an Ubuntu Linux \texttt{Bash} Terminal.
For your personal machines,  on a Mac you will use \texttt{term}
and \texttt{GitBash} under Windows.

Follow the directions on the GitLab project webpage, and answer the questions below.

{\bf NOTE: Access https://student-gitlab.pcs.cnu.edu  NOT gitlab.com or github.com}

\vspace{2in}

\section{Questions}

Answer or initial that you completed as directed.

\begin{enumerate}
\item Part 1 - File/Directory Structure and Bash
	\begin{enumerate}
	\item \initial Initial when you have opened the File Explorer GUI and navigated to the Documents folder.
	\item \initial Initial when you have navigated to the Home folder in File Explorer.
	\item \initial Initial when you have navigated back to the Desktop folder in File Explorer.
	\item \initial Initial when you have opened the Terminal Command Line Interface.
	\item What is another name for a CLI?  $\rule{4cm}{0.15mm}$
	\item \initial Initial when you have listed files using \texttt{ls}.
	\item \initial Initial when you have listed files using \texttt{ls -altr}.
	\item \initial Initial when you have changed to the \texttt{Documents} directory in the Bash terminal and confirmed with \texttt{pwd}.
	\item \initial Initial when you have changed back to the Home directory in the Bash terminal.
	\item \initial Initial when you have changed to the \texttt{Desktop} directory in the Bash terminal and confirmed with \texttt{pwd}.
	\item What is the full path of the Desktop directory?\\ $\rule{8cm}{0.15mm}$
	\item \initial Initial when you have created the \texttt{cs250L} folder on your Desktop using Bash commands in your terminal.
	\item \initial Initial after using \texttt{ls} to see new folder listed in Bash terminal AND in Files GUI.
	\item \initial Initial after using \texttt{ls -altr} to see in list form.
	\item \initial Initial after doing \texttt{cd ..} with \texttt{pwd} confirmation.

	\item \initial Initial when you have navigated to the root directory in Bash.
	\item \initial Initial after doing a \texttt{ls etc} to show contents of \texttt{/etc} folder.
	\item \initial Initial after doing a \texttt{ls -altr  /etc} to show contents of \texttt{/etc} folder.
	\item \initial Initial when you have navigated back to the Desktop directory going step by step.
	\item What is the command used to back up one directory from the current directory?\\
	$\rule{8cm}{0.15mm}$
	\item What is the full path of the current directory after backing up one from the Desktop directory?\\ $\rule{8cm}{0.15mm}$
	\item What is the command used to create a new directory in a bash shell?\\
	$\rule{4cm}{0.15mm}$
	\item What is the command used to display the current directory?\\
	$\rule{4cm}{0.15mm}$
	\item What is the command used to go to a user's home directory (denoted with \textasciitilde) ?\\
	$\rule{4cm}{0.15mm}$
	\item What is the shortcut that enables us to avoid typing out the full \texttt{cd Desktop} (or any other file or directory name) every time?\\
	$\rule{6cm}{0.15mm}$

	\end{enumerate}
\vspace{0.5cm}
\item Part 2 - Git Project

	Follow directions on README, and the provided Workflow slides to complete the simple coding project using Git, GitLab, and Web-CAT.


	\begin{enumerate}
	\item \initial Initial when you have set your `WCUSER` and `WCPASS` variables for WebCAT on personal GitLab \textbf{group}.
	\item \initial Initial when you have forked \textbf{lab01-s24} project repo to your \textbf{personal} group.
	\item \initial Initial when you have set your Git credentials.
	\item \initial when you have cloned \textbf{lab01-s24} project repo into your \texttt{cpsc250L} directory AND verified its contents using \texttt{ls}.
	\item What is the full path of the repo directory that you just cloned?\\ $\rule{10cm}{0.15mm}$
	\item \initial Initial when you have the project open in PyCharm.
	\item \initial Initial when you set the working directory in PyCharm.
	\item \initial Initial when you make the first \texttt{push} to GitLab.
	\item \initial Initial when Exercise 1 is complete and pushed
	\item \initial Initial when you have verified partial correctness on WebCAT!
	\item \initial Initial when Exercise 2 is complete and pushed
	\item \initial Initial when you have verified correct on WebCAT!
	\item After completing this lab, what \textbf{two} things should you add to your resume? \\
	$\rule{6cm}{0.15mm}$ , $\rule{6cm}{0.15mm}$

	\end{enumerate}
\end{enumerate}

If all is initialed and filled out, and correct on WebCAT, then
show your instructor and hand in this form.

You are then free to leave; have a great remainder of the day.
Of course your day should include some additional coding practice!

This lab is worth 100 points:
\begin{itemize}
 \item 35 points completing this worksheet
 \item 35 points WebCAT solution (correctness)
 \item 30 points lab participation (completing during lab or significant progress)
 \item \initial \textbf{Instructor} initial before leaving lab period
\end{itemize}


\end{document}
